---
title: "Machine Learning Assignment 3"
author: "AKANKSHA NADUKULA"
date: '2022-10-15'
output: pdf_document
---

```{r setup}
UniversalBank = read.csv("C:/Users/gauth/Downloads/UniversalBank (2).csv")
summary(UniversalBank)
```
```{r}
library(caret)
library(ISLR)
library(dplyr)
library(class)
library(e1071)
library(reshape)
library(reshape2)
```
```{R}
df= UniversalBank

#converting variables
UniversalBank$Personal.Loan <- factor(UniversalBank$Personal.Loan)
UniversalBank$Online <- factor(UniversalBank$Online)
UniversalBank$CreditCard <- factor(UniversalBank$CreditCard)
```

```{R}
#TASK1
set.seed(64060)
train.index <- createDataPartition(df$Personal.Loan, p =0.6, list = FALSE)
train.df = df[train.index,]
validation.df = df[-train.index,]


mytable <- xtabs(~ CreditCard + Online + Personal.Loan , data = train.df)
ftable(mytable)
```

```{r}
#TASK2
#The probability of loan acceptance (Loan = 1) conditional on having a bank 
#credit card (CC = 1) and being an active user of online banking services 
#(Online = 1)
#Probability of Loan acceptance given having a bank credit card and user
Probability = (50/(50+477))
Probability
```


```{r}
#Task3
table(Personal.Loan = train.df$Personal.Loan, Online = train.df$Online)

table(Personal.Loan = train.df$Personal.Loan, CreditCard = train.df$CreditCard)
table(Personal.Loan = train.df$Personal.Loan)
```

```{r}

#TASK4
#i. P(CC = 1 | Loan = 1) (the proportion of credit card holders among the loan 
#acceptors) 
Probability1 <- 85/(85+200)
Probability1

#ii. P(Online = 1 | Loan = 1)  
Probability2 <- 174/(174+111)
Probability2

#iii. P(Loan = 1) (the proportion of loan acceptors)  
Probability3 <- 285/(285+2715)
Probability3
#iv. P(CC = 1 | Loan = 0)  
Probability4 <- 784/(784+1931)
Probability4

#v. P(Online = 1 | Loan = 0) 
Probability5 <- 1621/(1621+1094)
Probability5

#vi. P(Loan = 0) 
Probability6 <- 2715/(2715+285)
Probability6
```

```{r}
#Task 5  
#Use the quantities computed above to compute the naive Ba1 probability 
#P(Loan = 1 | CC = 1, Online = 1).
Task5Probability <- (Probability1*Probability2*Probability3)/((Probability1*
                                    Probability2*Probability3)+(Probability4*Probability5*Probability6))
Task5Probability
```


Task6
Compare this value with the one obtained from the pivot table in (B). Which is 
a more accurate estimate?
The value derived in 2 was 0.09487666 and in the Task 5 is 0.09980052. There is 
not much difference in the derived values as there is not much difference in 
the methods. The only difference between the exact method and the naive-baise 
method is the exact method would need the the exact same independent variable classifications to predict, whereas the #naive bayes method does not. We can 
say that the value derived from the Task 2 is more #accurate as we have taken 
the exact values from the pivot table.


```{r}
#Task7
#Run naive Bayes on the data. Examine the model output on training data, and 
#find the entry that corresponds to P(Loan = 1 | CC = 1, Online = 1).
#Compare this to the number you obtained in (E). 

nb.model<-naiveBayes (Personal.Loan~ Online +CreditCard, data=train.df) 
To_Predict=data.frame(Online= 1, CreditCard= 1) 
predict(nb.model,To_Predict,type='raw')

    
```

The value derived from the Task 7 is 0.1013226 and the value derived from the Task 
5 is 0.09980052. The values are almost alike. There is only a minute difference 
because of the rounding. The difference will not affect the rank order of the ouput. 
